---
title: "Assignment 4"
author: "Lucas Ho"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\[
10/10
\]

# Question 1
## Part a
```{r}
data <- read.csv("NZBIRDS.csv")
sam <- sample(nrow(data), 35)
rand_sam <- data[sam, ]
rand_sam
```

## Part b
```{r}
t.test(rand_sam$Body.Mass)
```

\[
(-38.3708, 13350.3708)
\]

## Part c

If a 95% confidence interval for a parameter $\theta$ is (-38.3708, 13350.3708), then we are 95% "confident" that $\theta$ falls between -38.3708 and 13350.3708.

## Part d

The mean from the MINITAB, 9113, is within the 95% confidence interval (-38.3708, 13350.3708). 

## Part e

```{r}
t.test(rand_sam$Egg.Length)
```

\[
(46.0380, 74.4191)
\]

If a 95% confidence interval for a parameter $\theta$ is (46.0380, 74.4191), then we are 95% "confident" that $\theta$ falls between 46.0380 and 74.4191.

# Question 2
## Part a
```{r}
set.seed(10); y1 <- rnorm(100, mean = 1312, sd = 422)
set.seed(20); y2 <- rnorm(47, mean = 1352, sd = 271)
t.test(y1, y2, var.equal = FALSE, conf.level = 0.9)
```

\[
(-137.9459, 52.4098)
\]

## Part b
```{r}
var.test(y1, y2)
```

\[
(1.2608, 2.9122)
\]

Based off the interval, 1 is not within the 90% confidence interval, which provides evidence that the two populations do not have similar variances.

# Question 3

Pivotal statistic for the normal distribution is $Z = \frac{y}{\sigma}$

Pivotal statistic for the chi-square distribution for 1 degree of freedom is $\chi^2 = (\frac{y}{\sigma})^2$

This shows the relation between the normal distribution and chi-squared distribution for 1 degree of freedom.

# Question 4
## Part a
\[
H_0: \mu = 2, H_a: \mu \neq 2
\]

## Part b
```{r}
y <- read.csv("ROUGHPIPE.csv")
t.test(y, mu = 2)
```

\[
t = -1.0158, p-value = 0.3225
\]

## Part c
\[
<1.636, >2.126
\]

## Part d

The p-value is 0.3225 which does not provide evidence to reject that the means of the piper differ from 2

## Part e

The rejection region is the values that are not within the confidence interval

# Question 5
## Part a
```{r}
y <- read.csv("WISCLAKES.csv")
t.test(y$DOC, mu = 15)
```

## Part b
```{r}
theta.null = mean(y$DOC) + qnorm(0.05) * sd(y$DOC)
theta.alt = 14
pnorm((theta.null - theta.alt)/ sd(y$DOC), lower.tail = FALSE)
```

# Question 6
```{r}
library(dplyr)
data <- read.csv("ORCHARD.csv")
fog <- data %>% filter(CONDITION == "FOG")
cl <- data %>% filter(CONDITION == "CLEAR" | CONDITION == "CLOUDY")
t.test(fog$RATIO, cl$RATIO, var.equal = TRUE)
```

# Question 7
## Part a
```{r}
data <- read.csv("GASTURBINE.csv")
trad <- data %>% filter(ENGINE == "Traditional")
aero <- data %>% filter(ENGINE == "Aeroderiv")
t.test(trad$HEATRATE, aero$HEATRATE, var.equal = TRUE)
```

## Part b
```{r}
adv <- data %>% filter(ENGINE == "Advanced")
t.test(adv$HEATRATE, aero$HEATRATE, var.equal = TRUE)
```

# Question 8
## Part a
\[
H_0: \mu_1 = \mu_2, H_a: \mu_1 \neq \mu_2
\]

## Part b
```{r}
data <- read.csv("GOBIANTS.csv")
gobi <- data %>% filter(Region == "Gobi Desert")
dry <- data %>% filter(Region == "Dry Steppe")
t.test(gobi$AntSpecies, dry$AntSpecies)
```

## Part c
\[
<-30.0478, >25.7145
\]

## Part d
\[
0.8622
\]

## Part e

There is not enough evidence to reject the notion that the two sites have differing means

## Part f

Independent, Normal distribution, Random

# Question 9
```{r}
data <- read.csv("THRUPUT.csv")
t.test(data$HUMAN, data$AUTO)
```

# Question 10
```{r}
set.seed(35); sam <- round(rnorm(30, 20, 3), 3)
myboot<-function(iter=10000,x,fun="mean",alpha=0.05,...){  #Notice where the ... is repeated in the code
n=length(x)   #sample size

y=sample(x,n*iter,replace=TRUE)
rs.mat=matrix(y,nr=n,nc=iter,byrow=TRUE)
xstat=apply(rs.mat,2,fun) # xstat is a vector and will have iter values in it 
ci=quantile(xstat,c(alpha/2,1-alpha/2))# Nice way to form a confidence interval
# A histogram follows
# The object para will contain the parameters used to make the histogram
para=hist(xstat,freq=FALSE,las=1,
main=paste("Histogram of Bootstrap sample statistics","\n","alpha=",alpha," iter=",iter,sep=""),
...)

#mat will be a matrix that contains the data, this is done so that I can use apply()
mat=matrix(x,nr=length(x),nc=1,byrow=TRUE)

#pte is the point estimate
#This uses whatever fun is
pte=apply(mat,2,fun)
abline(v=pte,lwd=3,col="Black")# Vertical line
segments(ci[1],0,ci[2],0,lwd=4)      #Make the segment for the ci
text(ci[1],0,paste("(",round(ci[1],2),sep=""),col="Red",cex=3)
text(ci[2],0,paste(round(ci[2],2),")",sep=""),col="Red",cex=3)

# plot the point estimate 1/2 way up the density
text(pte,max(para$density)/2,round(pte,2),cex=3)

return(list(ci=ci,fun=fun,x=x))# Some output to use if necessary
}

myboot(x = sam)