---
title: "Lab 8"
author: "Lucas Ho"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Task 1
```{r}
getwd()
```

# Task 2
```{r}
unif <- runif(10, 0, 5)

pmu = (0 + 5) / 2

pvar = ((5 - 0)^2) / 12

smu <- mean(unif)

svar <- sd(unif)^2
```

Line A creates a vector for a random uniform distribution sample

Line B creates a matrix of data in table form for the uniform distribution

Line C applies a function to sum all the data of each row

Line D stores the output of the function into a vector w

# Task 3
```{r}
mycltu=function(n,iter,a=0,b=10){
  ## r-random sample from the uniform
  y=runif(n*iter,a,b)
  ## Place these numbers into a matrix
  ## The columns will correspond to the iteration and the rows will equal the sample size n
  data=matrix(y,nr=n,nc=iter,byrow=TRUE)
  ## apply the function mean to the columns (2) of the matrix
  ## these are placed in a vector w
  w=apply(data,2,mean)
  ## We will make a histogram of the values in w
  ## How high should we make y axis?
  ## All the values used to make a histogram are placed in param (nothing is plotted yet)
  param=hist(w,plot=FALSE)
  ## Since the histogram will be a density plot we will find the max density
  
  ymax=max(param$density)
  ## To be on the safe side we will add 10% more to this
  ymax=1.1*ymax
  ## Now we can make the histogram
  hist(w,freq=FALSE,  ylim=c(0,ymax), main=paste("Histogram of sample mean",
                                                 "\n", "sample size= ",n,sep=""),xlab="Sample mean")
  ## add a density curve made from the sample distribution
  lines(density(w),col="Blue",lwd=3) # add a density plot
  ## Add a theoretical normal curve 
  curve(dnorm(x,mean=(a+b)/2,sd=(b-a)/(sqrt(12*n))),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
  ## Add the density from which the samples were taken
  curve(dunif(x,a,b),add=TRUE,lwd=4)
  
}

mycltu(1, 10000)
mycltu(2, 10000)
mycltu(3, 10000)
mycltu(5, 10000)
mycltu(10, 10000)
mycltu(30, 10000)
```

Appears closer to a normal distribution as the sample size increases

# Task 4
```{r}
mycltb=function(n,iter,p=0.3,...){
  
  ## r-random sample from the Binomial
  y=rbinom(n*iter,size=n,prob=p)
  ## Place these numbers into a matrix
  ## The columns will correspond to the iteration and the rows will equal the sample size n
  data=matrix(y,nr=n,nc=iter,byrow=TRUE)
  ## apply the function mean to the columns (2) of the matrix
  ## these are placed in a vector w
  w=apply(data,2,mean)
  ## We will make a histogram of the values in w
  ## How high should we make y axis?
  ## All the values used to make a histogram are placed in param (nothing is plotted yet)
  param=hist(w,plot=FALSE)
  ## Since the histogram will be a density plot we will find the max density
  
  ymax=max(param$density)
  ## To be on the safe side we will add 10% more to this
  ymax=1.1*ymax
  
  ## Now we can make the histogram
  ## freq=FALSE means take a density
  hist(w,freq=FALSE,  ylim=c(0,ymax),
       main=paste("Histogram of sample mean","\n", "sample size= ",n,sep=""),
       xlab="Sample mean",...)
  ## add a density curve made from the sample distribution
  #lines(density(w),col="Blue",lwd=3) # add a density plot
  ## Add a theoretical normal curve 
  curve(dnorm(x,mean=n*p,sd=sqrt(p*(1-p))),add=TRUE,col="Red",lty=2,lwd=3) 
  
}

mycltb(4, 10000)
mycltb(5, 10000)
mycltb(10, 10000)
mycltb(20, 10000)

mycltb(4, 10000, p=0.7)
mycltb(5, 10000, p=0.7)
mycltb(10, 10000, p=0.7)
mycltb(20, 10000, p=0.7)

mycltb(4, 10000, p=0.5)
mycltb(5, 10000, p=0.5)
mycltb(10, 10000, p=0.5)
mycltb(20, 10000, p=0.5)
```

Appears closer to a normal distribution about the binomial mean as the sample size increases

# Task 5
```{r}
mycltp=function(n,iter,lambda=10,...){
  
  ## r-random sample from the Poisson
  y=rpois(n*iter,lambda=lambda)
  ## Place these numbers into a matrix
  ## The columns will correspond to the iteration and the rows will equal the sample size n
  data=matrix(y,nr=n,nc=iter,byrow=TRUE)
  ## apply the function mean to the columns (2) of the matrix
  ## these are placed in a vector w
  w=apply(data,2,mean)
  ## We will make a histogram of the values in w
  ## How high should we make y axis?
  ## All the values used to make a histogram are placed in param (nothing is plotted yet)
  param=hist(w,plot=FALSE)
  ## Since the histogram will be a density plot we will find the max density
  
  ymax=max(param$density)
  ## To be on the safe side we will add 10% more to this
  ymax=1.1*ymax
  
  ## Make a suitable layout for graphing
  layout(matrix(c(1,1,2,3),nr=2,nc=2, byrow=TRUE))
  
  ## Now we can make the histogram
  hist(w,freq=FALSE,  ylim=c(0,ymax), col=rainbow(max(w)),
       main=paste("Histogram of sample mean","\n", "sample size= ",n," iter=",iter," lambda=",lambda,sep=""),
       xlab="Sample mean",...)
  ## add a density curve made from the sample distribution
  #lines(density(w),col="Blue",lwd=3) # add a density plot
  ## Add a theoretical normal curve 
  curve(dnorm(x,mean=lambda,sd=sqrt(lambda/n)),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
  
  # Now make a new plot
  # Since y is discrete we should use a barplot
  barplot(table(y)/(n*iter),col=rainbow(max(y)), main="Barplot of sampled y", ylab ="Rel. Freq",xlab="y" )
  x=0:max(y)
  plot(x,dpois(x,lambda=lambda),type="h",lwd=5,col=rainbow(max(y)),
       main="Probability function for Poisson", ylab="Probability",xlab="y")
}

mycltp(2, 10000, 4)
mycltp(3, 10000, 4)
mycltp(5, 10000, 4)
mycltp(10, 10000, 4)
mycltp(20, 10000, 4)

mycltp(2, 10000)
mycltp(3, 10000)
mycltp(5, 10000)
mycltp(10, 10000)
mycltp(20, 10000)
```

<video controls="controls" width="800" height="600" name="Video Name">
  <source src="/Users/lucasho/Desktop/task5_lab8.mov">
</video>

# Task 6
```{r}
MATH4753LHO24::mycltb(5, 10000, 0.3)
```